Quantum Hoare Type Theory

### 2020-04-30 ms-paper/ms-paper.tex
The pair types need to be revised; subsubsection was missing mysteriously

\subsubsection*{Hello Quantum World}
\begin{lstlisting}[language=QHaskell]
hqw : {emp} r : Bool {emp /\ Id(r, false)}
    = do q <= mkQbit false;
         measQbit q
\end{lstlisting}

We start out in an empty state and assert that the result is equal to \texttt{false}.

\subsubsection*{Coin Toss}
\begin{lstlisting}[language=QHaskell]
rnd : {emp} r : Bool {emp}
    = do q <= mkQbit false;
         applyU (H q);
         measQbit q
\end{lstlisting}

As the result can be in either of its two values \texttt{false} or \texttt{true}, we need not specify any special postcondition as type checking the result will be sufficient for correctness.

\subsubsection*{Testing Bell Pair}
\begin{lstlisting}[language=QHaskell]
testBell : {emp} (a, b) : (Bool, Bool) {emp /\ Id(a, b)}  -- a,b \in {true, false}
         = do qa <= mkQbit false;
              applyU (H qa);
              qb <= mkQbit false;
              applyU (ifQ qa (X qb));
              (measQbit qa, measQbit qb)
\end{lstlisting}

Here, we are asserting that the returned booleans $a$ and $b$ hold the same value, which is what we expect from a Bell pair.

@@

\subsection{Bell pair}
\begin{lstlisting}[language=QHaskell]
bell : {emp} (a, b) : (Qbit, Qbit) {Id(a, b) /\ a \in {|0\>, |1\>}}
     = do qa <- qplus;
          qb <- share qa;
          return (qa, qb)
\end{lstlisting}

>>>>

\subsubsection*{Hello Quantum World}
We start out in an empty state and assert that the result is equal to \texttt{false}.
\begin{lstlisting}[language=QHaskell]
hqw : {emp} r : Bool {emp /\ Id(r, false)}
    = do q <= mkQbit false;
         measQbit q
\end{lstlisting}

\subsubsection*{Coin Toss}
As the result can be in either of its two values \texttt{false} or \texttt{true}, we need not specify any special postcondition as type checking the result will be sufficient for correctness.

\begin{lstlisting}[language=QHaskell]
rnd : {emp} r : Bool {emp}
    = do q <= mkQbit false;
         applyU (H q);
         measQbit q
\end{lstlisting}

\subsubsection*{Testing Bell Pair}
Here, we are asserting that the returned booleans $a$ and $b$ hold the same value, which is what we expect from a Bell pair.

\todo{The type should be \type{Bool} $\otimes$ \type{Bool}}
\begin{lstlisting}[language=QHaskell]
testBell : {emp} (a, b) : (Bool, Bool) {emp /\ Id(a, b)}  -- a,b \in {true, false}
         = do qa <= mkQbit false;
              applyU (H qa);
              qb <= mkQbit false;
              applyU (ifQ qa (X qb));
              (measQbit qa, measQbit qb)
\end{lstlisting}

@@

\subsection{Bell pair}
\todo{The type should be \type{Qbit} $\otimes$ \type{Qbit}}
\begin{lstlisting}[language=QHaskell]
bell : {emp} (a, b) : (Qbit, Qbit) {Id(a, b) /\ a \in {|0\>, |1\>}}
     = do qa <- qplus;
          qb <- share qa;
          return (qa, qb)
\end{lstlisting}
